Defining properties regulating pioneer-factor binding and function

### 2023-01-18 manuscript/manuscript_sections/_06_Figure_Legends.qmd

-   examples of class IV-VII regions

@@

@@

@@

-   New binding sites at higher expression levels

-   Zld DBD ChIP only at CAGGTAG sites

>>>>

-   examples of class IV-VI regions

@@

-   Individual examples of sites that are gained in taz-treated cells

@@

-   FL and DBD preference for motifs that are in open vs. closed chromatin: % of closed vs. open motifs bound, motif scores for accessible bound, accessible unbound, inaccessible bound, and inaccessible unbound.

@@

-   Analysis of deep learning models
